Radio Emission from Red-Giant Hot Jupiters

### 2015-09-29 ms.tex
renamed figure 3

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{figure*}[bp]
	\plotonesc{radio_emission_ChristensenAubert_multiplecriteria.pdf}
   \caption{Radio flux in unit of Jy from a planetary companion to a red giant with mass loss rate $10^{-8} M_{\odot }/\mbox{yr}$ (top) and that to an AGB star with mass loss rate $10^{-5} M_{\odot }/\mbox{yr}$ (bottom). The systems are located at 100 pc away. The doubly hatched regions show the parameter spaces where the planetary radio emission would not be observable at all because the maximum frequency of the emission (cyclotron frequency at the planetary surface, $\nu_{\rm cyc}$) is below the plasma frequency cut-off, $\nu_{\rm plasma}^{\rm los}$. The regions hatched with vertical lines show the parameter spaces where the frequencies of bulk radio emission is below $\nu_{\rm plasma}^{\rm los}$, i.e., $\nu_{\rm plasma}^{\rm los} > 0.1 \nu_{\rm cyc}$)}
  \label{fig:radio}
\end{figure*}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

\newpage

>>>>

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{figure*}[bp]
	\plotonesc{radio_emission_mass_orbit.pdf}
   \caption{Radio flux in unit of Jy from a planetary companion to a red giant with mass loss rate $10^{-8} M_{\odot }/\mbox{yr}$ (top) and that to an AGB star with mass loss rate $10^{-5} M_{\odot }/\mbox{yr}$ (bottom). The systems are located at 100 pc away. The doubly hatched regions show the parameter spaces where the planetary radio emission would not be observable at all because the maximum frequency of the emission (cyclotron frequency at the planetary surface, $\nu_{\rm cyc}$) is below the plasma frequency cut-off, $\nu_{\rm plasma}^{\rm los}$. The regions hatched with vertical lines show the parameter spaces where the frequencies of bulk radio emission is below $\nu_{\rm plasma}^{\rm los}$, i.e., $\nu_{\rm plasma}^{\rm los} > 0.1 \nu_{\rm cyc}$)}
  \label{fig:radio}
\end{figure*}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

\begin{thebibliography}{}
\expandafter\ifx\csname natexlab\endcsname\relax\def\natexlab#1{#1}\fi

\bibitem[{{Auri{\`e}re} {et~al.}(2015){Auri{\`e}re}, {Konstantinova-Antova},
  {Charbonnel}, {Wade}, {Tsvetkova}, {Petit}, {Dintrans}, {Drake}, {Decressin},
  {Lagarde}, {Donati}, {Roudier}, {Ligni{\`e}res}, {Schr{\"o}der},
  {Landstreet}, {L{\`e}bre}, {Weiss}, \& {Zahn}}]{auriere2015}
{Auri{\`e}re}, M., {Konstantinova-Antova}, R., {Charbonnel}, C., {et~al.} 2015,
  \aap, 574, A90

\bibitem[{{Bastian}(1990)}]{Bastian1990}
{Bastian}, T.~S. 1990, \solphys, 130, 265

\bibitem[{{Bastian} {et~al.}(2000){Bastian}, {Dulk}, \&
  {Leblanc}}]{bastian2000}
{Bastian}, T.~S., {Dulk}, G.~A., \& {Leblanc}, Y. 2000, \apj, 545, 1058

\bibitem[{{Beasley} {et~al.}(1992){Beasley}, {Stewart}, \&
  {Carter}}]{Beasley1992}
{Beasley}, A.~J., {Stewart}, R.~T., \& {Carter}, B.~D. 1992, \mnras, 254, 1

\bibitem[{{Burrows} {et~al.}(2001){Burrows}, {Hubbard}, {Lunine}, \&
  {Liebert}}]{burrows_et_al2001}
{Burrows}, A., {Hubbard}, W.~B., {Lunine}, J.~I., \& {Liebert}, J. 2001,
  Reviews of Modern Physics, 73, 719

\bibitem[{{Busse}(1976)}]{busse1976}
{Busse}, F.~H. 1976, Physics of the Earth and Planetary Interiors, 12, 350

\bibitem[{{Christensen}(2010)}]{christensen2010}
{Christensen}, U.~R. 2010, \ssr, 152, 565

\bibitem[{{Christensen} \& {Aubert}(2006)}]{christensen2006}
{Christensen}, U.~R., \& {Aubert}, J. 2006, Geophysical Journal International,
  166, 97

\bibitem[{{Christensen} {et~al.}(2009){Christensen}, {Holzwarth}, \&
  {Reiners}}]{christensen_et_al2009}
{Christensen}, U.~R., {Holzwarth}, V., \& {Reiners}, A. 2009, \nat, 457, 167

\bibitem[{{Condon}(1974)}]{Condon1974}
{Condon}, J.~J. 1974, \apj, 188, 279

\bibitem[{{Condon} \& {Ransom}(2016)}]{condon+ransom2016}
{Condon}, J.~J., \& {Ransom}, S.~M. 2016, {Essential Radio Astronomy (Princeton
  Series in Modern Observational Astronomy)} (Princeton Series in Modern
  Observational Astronomy, Princeton University Press, 2016)

\bibitem[{{Condon} {et~al.}(2012){Condon}, {Cotton}, {Fomalont}, {Kellermann},
  {Miller}, {Perley}, {Scott}, {Vernstrom}, \& {Wall}}]{Condon2012}
{Condon}, J.~J., {Cotton}, W.~D., {Fomalont}, E.~B., {et~al.} 2012, \apj, 758,
  23

\bibitem[{{Desch} \& {Kaiser}(1984)}]{desch+kaiser1984}
{Desch}, M.~D., \& {Kaiser}, M.~L. 1984, \nat, 310, 755

\bibitem[{{Dessler}(1983)}]{dessler1983}
{Dessler}, A.~J. 1983, {Physics of the Jovian magnetosphere}

\bibitem[{{Drake} \& {Linsky}(1986)}]{drake1986}
{Drake}, S.~A., \& {Linsky}, J.~L. 1986, \aj, 91, 602

\bibitem[{{Drake} {et~al.}(1987){Drake}, {Linsky}, \& {Elitzur}}]{drake1987}
{Drake}, S.~A., {Linsky}, J.~L., \& {Elitzur}, M. 1987, \aj, 94, 1280

\bibitem[{{Dumm} \& {Schild}(1998)}]{dumm1998}
{Dumm}, T., \& {Schild}, H. 1998, New Astronomy, 3, 137

\bibitem[{{Farrell} {et~al.}(1999){Farrell}, {Desch}, \& {Zarka}}]{farrell1999}
{Farrell}, W.~M., {Desch}, M.~D., \& {Zarka}, P. 1999, \jgr, 104, 14025

\bibitem[{{Fite} \& {Brackmann}(1958)}]{fite1958}
{Fite}, W.~L., \& {Brackmann}, R.~T. 1958, Physical Review, 112, 1141

\bibitem[{{Fix} \& {Spangler}(1976)}]{Fix1976}
{Fix}, J.~D., \& {Spangler}, S.~R. 1976, \apj, 209, 503

\bibitem[{{Fortney} {et~al.}(2007){Fortney}, {Marley}, \&
  {Barnes}}]{fortney2007}
{Fortney}, F.~J., {Marley}, M.~S., \& {Barnes}, J.~W. 2007, \apj, 659, 1661

\bibitem[{{George} \& {Stevens}(2007)}]{george2007}
{George}, S.~J., \& {Stevens}, I.~R. 2007, \mnras, 382, 455

\bibitem[{{Grie{\ss}meier} {et~al.}(2005){Grie{\ss}meier}, {Motschmann},
  {Mann}, \& {Rucker}}]{griesmeier2005}
{Grie{\ss}meier}, J.-M., {Motschmann}, U., {Mann}, G., \& {Rucker}, H.~O. 2005,
  \aap, 437, 717

\bibitem[{{Grie{\ss}meier} {et~al.}(2007{\natexlab{a}}){Grie{\ss}meier},
  {Preusse}, {Khodachenko}, {Motschmann}, {Mann}, \&
  {Rucker}}]{griesmeier2007a}
{Grie{\ss}meier}, J.-M., {Preusse}, S., {Khodachenko}, M., {et~al.}
  2007{\natexlab{a}}, \planss, 55, 618

\bibitem[{{Grie{\ss}meier} {et~al.}(2007{\natexlab{b}}){Grie{\ss}meier},
  {Zarka}, \& {Spreeuw}}]{griesmeier2007b}
{Grie{\ss}meier}, J.-M., {Zarka}, P., \& {Spreeuw}, H. 2007{\natexlab{b}},
  \aap, 475, 359

\bibitem[{{Grie{\ss}meier} {et~al.}(2004){Grie{\ss}meier}, {Stadelmann},
  {Penz}, {Lammer}, {Selsis}, {Ribas}, {Guinan}, {Motschmann}, {Biernat}, \&
  {Weiss}}]{griesmeier2004}
{Grie{\ss}meier}, J.-M., {Stadelmann}, A., {Penz}, T., {et~al.} 2004, \aap,
  425, 753

\bibitem[{{Hallinan} {et~al.}(2013){Hallinan}, {Sirothia}, {Antonova},
  {Ishwara-Chandra}, {Bourke}, {Doyle}, {Hartman}, \& {Golden}}]{hallinan2013}
{Hallinan}, G., {Sirothia}, S.~K., {Antonova}, A., {et~al.} 2013, \apj, 762, 34

\bibitem[{{Hicks} {et~al.}(2012){Hicks}, {Paravastu-Dalal}, {Stewart},
  {Erickson}, {Ray}, {Kassim}, {Burns}, {Clarke}, {Schmitt}, {Craig},
  {Hartman}, \& {Weiler}}]{Hicks2012}
{Hicks}, B.~C., {Paravastu-Dalal}, N., {Stewart}, K.~P., {et~al.} 2012, \pasp,
  124, 1090

\bibitem[{{Hundhausen}(1997)}]{hundhausen1997}
{Hundhausen}, A.~J. 1997, in Cosmic Winds and the Heliosphere, ed. J.~R.
  {Jokipii}, C.~P. {Sonett}, \& M.~S. {Giampapa}, 259

\bibitem[{{Ignace} {et~al.}(2010){Ignace}, {Giroux}, \&
  {Luttermoser}}]{ignace2010}
{Ignace}, R., {Giroux}, M.~L., \& {Luttermoser}, D.~G. 2010, \mnras, 402, 2609

\bibitem[{{Joy} {et~al.}(2002){Joy}, {Kivelson}, {Walker}, {Khurana},
  {Russell}, \& {Ogino}}]{joy2002}
{Joy}, S.~P., {Kivelson}, M.~G., {Walker}, R.~J., {et~al.} 2002, Journal of
  Geophysical Research (Space Physics), 107, 1309

\bibitem[{{Kassim} {et~al.}(2015){Kassim}, {Clarke}, {Helmboldt}, {Ray},
  {Lane}, {Polisensky}, {Mroczkowski}, {Deneva}, {Hicks}, {Hyman}, {Brisken},
  {Perley}, {Owen}, \& {Intema}}]{Kassim2015IAU}
{Kassim}, N.~E., {Clarke}, T., {Helmboldt}, J., {et~al.} 2015, IAU General
  Assembly, 22, 53643

\bibitem[{{Kiss} {et~al.}(1999){Kiss}, {Szatm{\'a}ry}, {Cadmus}, \&
  {Mattei}}]{Kiss:1999aa}
{Kiss}, L.~L., {Szatm{\'a}ry}, K., {Cadmus}, Jr., R.~R., \& {Mattei}, J.~A.
  1999, \aap, 346, 542

\bibitem[{{Knapp} {et~al.}(1995){Knapp}, {Bowers}, {Young}, \&
  {Phillips}}]{Knapp1995}
{Knapp}, G.~R., {Bowers}, P.~F., {Young}, K., \& {Phillips}, T.~G. 1995, \apj,
  455, 293

\bibitem[{{Konstantinova-Antova} {et~al.}(2010){Konstantinova-Antova},
  {Auri{\`e}re}, {Charbonnel}, {Drake}, {Schr{\"o}der}, {Stateva}, {Alecian},
  {Petit}, \& {Cabanac}}]{konstantinova2010}
{Konstantinova-Antova}, R., {Auri{\`e}re}, M., {Charbonnel}, C., {et~al.} 2010,
  \aap, 524, A57

\bibitem[{{Konstantinova-Antova} {et~al.}(2013){Konstantinova-Antova},
  {Aur{\'{\i}}ere}, {Charbonnel}, {Wade}, {Kolev}, {Antov}, {Tsvetkova},
  {Schr{\"o}der}, {Drake}, {Petit}, {de Medeiros}, {L{\'e}bre}, {Zhilyaev},
  {Verlyuk}, {Svyatogorov}, {Gershberg}, {Lovkaya}, {Bogdanovski}, {Stateva},
  {Cabanac}, {Avgoloupis}, {Contadakis}, \& {Seiradakis}}]{konstantinova2013}
{Konstantinova-Antova}, R., {Aur{\'{\i}}ere}, M., {Charbonnel}, C., {et~al.}
  2013, Bulgarian Astronomical Journal, 19, 14

\bibitem[{{Lazio} {et~al.}(2004){Lazio}, {Farrell}, {Dietrick}, {Greenlees},
  {Hogan}, {Jones}, \& {Hennig}}]{lazio2004}
{Lazio}, W., T.~J., {Farrell}, W.~M., {Dietrick}, J., {et~al.} 2004, \apj, 612,
  511

\bibitem[{{Lecavelier des Etangs} {et~al.}(2013){Lecavelier des Etangs},
  {Sirothia}, {Gopal-Krishna}, \& {Zarka}}]{lecavelier_et_al2013}
{Lecavelier des Etangs}, A., {Sirothia}, S.~K., {Gopal-Krishna}, \& {Zarka}, P.
  2013, \aap, 552, A65

\bibitem[{{Lim} {et~al.}(1998){Lim}, {Carilli}, {White}, {Beasley}, \&
  {Marson}}]{Lim1998}
{Lim}, J., {Carilli}, C.~L., {White}, S.~M., {Beasley}, A.~J., \& {Marson},
  R.~G. 1998, \nat, 392, 575

\bibitem[{{Marley} {et~al.}(2007){Marley}, {Fortney}, {Hubickyj},
  {Bodenheimer}, \& {Lissauer}}]{marley2007}
{Marley}, M.~S., {Fortney}, J.~J., {Hubickyj}, O., {Bodenheimer}, P., \&
  {Lissauer}, J.~J. 2007, \apj, 655, 541

\bibitem[{{Mizutani} {et~al.}(1992){Mizutani}, {Yamamoto}, \&
  {Fujimura}}]{mizutani1992}
{Mizutani}, H., {Yamamoto}, T., \& {Fujimura}, A. 1992, Advances in Space
  Research, 12, 265

\bibitem[{{Murphy} {et~al.}(2015){Murphy}, {Bell}, {Kaplan}, {Gaensler},
  {Offringa}, {Lenc}, {Hurley-Walker}, {Bernardi}, {Bowman}, {Briggs},
  {Cappallo}, {Corey}, {Deshpande}, {Emrich}, {Goeke}, {Greenhill}, {Hazelton},
  {Hewitt}, {Johnston-Hollitt}, {Kasper}, {Kratzenberg}, {Lonsdale}, {Lynch},
  {McWhirter}, {Mitchell}, {Morales}, {Morgan}, {Oberoi}, {Ord}, {Prabu},
  {Rogers}, {Roshi}, {Shankar}, {Srivani}, {Subrahmanyan}, {Tingay},
  {Waterson}, {Wayth}, {Webster}, {Whitney}, {Williams}, \&
  {Williams}}]{murphy2015}
{Murphy}, T., {Bell}, M.~E., {Kaplan}, D.~L., {et~al.} 2015, \mnras, 446, 2560

\bibitem[{{Mustill} \& {Villaver}(2012)}]{mustill+villaver2012}
{Mustill}, A.~J., \& {Villaver}, E. 2012, ArXiv e-prints, arXiv:1210.0328

\bibitem[{{Newell} \& {Hjellming}(1982)}]{Newell1982}
{Newell}, R.~T., \& {Hjellming}, R.~M. 1982, \apjl, 263, L85

\bibitem[{{Nordhaus} \& {Spiegel}(2013)}]{nordhaus+spiegel2013}
{Nordhaus}, J., \& {Spiegel}, D.~S. 2013, \mnras, 432, 500

\bibitem[{{Nordhaus} {et~al.}(2010){Nordhaus}, {Spiegel}, {Ibgui}, {Goodman},
  \& {Burrows}}]{nordhaus_et_al2010}
{Nordhaus}, J., {Spiegel}, D.~S., {Ibgui}, L., {Goodman}, J., \& {Burrows}, A.
  2010, \mnras, 1164

\bibitem[{{Noyola} {et~al.}(2014){Noyola}, {Satyal}, \&
  {Musielak}}]{noyola2014}
{Noyola}, J.~P., {Satyal}, S., \& {Musielak}, Z.~E. 2014, \apj, 791, 25

\bibitem[{{O'Gorman} {et~al.}(2013){O'Gorman}, {Harper}, {Brown}, {Drake}, \&
  {Richards}}]{OGorman2013}
{O'Gorman}, E., {Harper}, G.~M., {Brown}, A., {Drake}, S., \& {Richards},
  A.~M.~S. 2013, \aj, 146, 98

\bibitem[{{Parsons} {et~al.}(2012){Parsons}, {Pober}, {McQuinn}, {Jacobs}, \&
  {Aguirre}}]{parsons_et_al2012}
{Parsons}, A., {Pober}, J., {McQuinn}, M., {Jacobs}, D., \& {Aguirre}, J. 2012,
  \apj, 753, 81

\bibitem[{{Parsons} {et~al.}(2010){Parsons}, {Backer}, {Foster}, {Wright},
  {Bradley}, {Gugliucci}, {Parashare}, {Benoit}, {Aguirre}, {Jacobs},
  {Carilli}, {Herne}, {Lynch}, {Manley}, \& {Werthimer}}]{parsons_et_al2010}
{Parsons}, A.~R., {Backer}, D.~C., {Foster}, G.~S., {et~al.} 2010, \aj, 139,
  1468

\bibitem[{{Pequignot} {et~al.}(1991){Pequignot}, {Petitjean}, \&
  {Boisson}}]{pequignot1991}
{Pequignot}, D., {Petitjean}, P., \& {Boisson}, C. 1991, \aap, 251, 680

\bibitem[{{Petit} {et~al.}(2013){Petit}, {Auri{\`e}re}, {Konstantinova-Antova},
  {Morgenthaler}, {Perrin}, {Roudier}, \& {Donati}}]{petit2013}
{Petit}, P., {Auri{\`e}re}, M., {Konstantinova-Antova}, R., {et~al.} 2013, in
  Lecture Notes in Physics, Berlin Springer Verlag, Vol. 857, Lecture Notes in
  Physics, Berlin Springer Verlag, ed. J.-P. {Rozelot} \& C.~. {Neiner}, 231

\bibitem[{{Pober} {et~al.}(2014){Pober}, {Liu}, {Dillon}, {Aguirre}, {Bowman},
  {Bradley}, {Carilli}, {DeBoer}, {Hewitt}, {Jacobs}, {McQuinn}, {Morales},
  {Parsons}, {Tegmark}, \& {Werthimer}}]{pober_et_al2014}
{Pober}, J.~C., {Liu}, A., {Dillon}, J.~S., {et~al.} 2014, \apj, 782, 66

\bibitem[{{Queloz} {et~al.}(2006){Queloz}, {Udry}, {Mayor}, {Benz}, {Cassen},
  {Guillot}, \& {Quirrenbach}}]{exoplanets2006}
{Queloz}, D., {Udry}, S., {Mayor}, M., {et~al.}, eds. 2006, {Extrasolar
  planets}

\bibitem[{{Reimers}(1975)}]{reimers1975}
{Reimers}, D. 1975, Memoires of the Societe Royale des Sciences de Liege, 8,
  369

\bibitem[{{Reiners} \& {Christensen}(2010)}]{reiners2010}
{Reiners}, A., \& {Christensen}, U.~R. 2010, \aap, 522, A13

\bibitem[{{Rogers} \& {Bowman}(2008)}]{Rogers+Bowman2008}
{Rogers}, A.~E.~E., \& {Bowman}, J.~D. 2008, \aj, 136, 641

\bibitem[{{Russell}(1978)}]{russel1978}
{Russell}, C.~T. 1978, \nat, 272, 147

\bibitem[{{Sano}(1993)}]{sano1993}
{Sano}, Y. 1993, Journal of geomagnetism and geoelectricity, 45, 65

\bibitem[{{Schild}(1989)}]{schild1989}
{Schild}, H. 1989, \mnras, 240, 63

\bibitem[{{Sch{\"o}ier} \& {Olofsson}(2001)}]{schoier2001}
{Sch{\"o}ier}, F.~L., \& {Olofsson}, H. 2001, \aap, 368, 969

\bibitem[{{Schr{\"o}der} \& {Cuntz}(2005)}]{schroder2005}
{Schr{\"o}der}, K.-P., \& {Cuntz}, M. 2005, \apjl, 630, L73

\bibitem[{{Schr{\"o}der} \& {Cuntz}(2007)}]{schroder2007}
---. 2007, \aap, 465, 593

\bibitem[{{Sirothia} {et~al.}(2014){Sirothia}, {Lecavelier des Etangs},
  {Gopal-Krishna}, {Kantharia}, \& {Ishwar-Chandra}}]{sirothia2014}
{Sirothia}, S.~K., {Lecavelier des Etangs}, A., {Gopal-Krishna}, {Kantharia},
  N.~G., \& {Ishwar-Chandra}, C.~H. 2014, \aap, 562, A108

\bibitem[{{Skinner} {et~al.}(1997){Skinner}, {Dougherty}, {Meixner}, {Bode},
  {Davis}, {Drake}, {Arens}, \& {Jernigan}}]{Skinner1997}
{Skinner}, C.~J., {Dougherty}, S.~M., {Meixner}, M., {et~al.} 1997, \mnras,
  288, 295

\bibitem[{{Spiegel}(2012)}]{spiegel2012}
{Spiegel}, D.~S. 2012, ArXiv e-prints

\bibitem[{{Spiegel} \& {Madhusudhan}(2012)}]{spiegel+madhusudhan2012}
{Spiegel}, D.~S., \& {Madhusudhan}, N. 2012, \apj, 756, 132

\bibitem[{{Starchenko} \& {Jones}(2002)}]{starchenko2002}
{Starchenko}, S.~V., \& {Jones}, C.~A. 2002, Icarus, 157, 426

\bibitem[{{Stevens}(2005)}]{stevens2005}
{Stevens}, I.~R. 2005, \mnras, 356, 1053

\bibitem[{{Stevenson}(1979)}]{stevenson1979}
{Stevenson}, D.~J. 1979, Geophysical and Astrophysical Fluid Dynamics, 12, 139

\bibitem[{{Stil} {et~al.}(2014){Stil}, {Keller}, {George}, \&
  {Taylor}}]{Stil2014}
{Stil}, J.~M., {Keller}, B.~W., {George}, S.~J., \& {Taylor}, A.~R. 2014, \apj,
  787, 99

\bibitem[{{Stroe} {et~al.}(2012){Stroe}, {Snellen}, \&
  {R{\"o}ttgering}}]{stroe2012}
{Stroe}, A., {Snellen}, I.~A.~G., \& {R{\"o}ttgering}, H.~J.~A. 2012, \aap,
  546, A116

\bibitem[{{Str{\"o}mgren}(1939)}]{stromgren1939}
{Str{\"o}mgren}, B. 1939, \apj, 89, 526

\bibitem[{{Suzuki}(2007)}]{suzuki2007}
{Suzuki}, T.~K. 2007, \apj, 659, 1592

\bibitem[{{Trifonov} {et~al.}(2015){Trifonov}, {Reffert}, {Zechmeister},
  {Reiners}, \& {Quirrenbach}}]{trifonov2015}
{Trifonov}, T., {Reffert}, S., {Zechmeister}, M., {Reiners}, A., \&
  {Quirrenbach}, A. 2015, ArXiv e-prints, arXiv:1508.04769

\bibitem[{{Tsvetkova} {et~al.}(2013){Tsvetkova}, {Petit}, {Auri{\`e}re},
  {Konstantinova-Antova}, {Wade}, {Charbonnel}, {Decressin}, \&
  {Bogdanovski}}]{tsvetkova2013}
{Tsvetkova}, S., {Petit}, P., {Auri{\`e}re}, M., {et~al.} 2013, \aap, 556, A43

\bibitem[{{van den Oord} \& {de Bruyn}(1994)}]{vandenOord1994}
{van den Oord}, G.~H.~J., \& {de Bruyn}, A.~G. 1994, \aap, 286, 181

\bibitem[{{van Haarlem} {et~al.}(2013){van Haarlem}, {Wise}, {Gunst}, {Heald},
  {McKean}, {Hessels}, {de Bruyn}, {Nijboer}, {Swinbank}, {Fallows},
  {Brentjens}, {Nelles}, {Beck}, {Falcke}, {Fender}, {H{\"o}randel},
  {Koopmans}, {Mann}, {Miley}, {R{\"o}ttgering}, {Stappers}, {Wijers},
  {Zaroubi}, {van den Akker}, {Alexov}, {Anderson}, {Anderson}, {van Ardenne},
  {Arts}, {Asgekar}, {Avruch}, {Batejat}, {B{\"a}hren}, {Bell}, {Bell}, {van
  Bemmel}, {Bennema}, {Bentum}, {Bernardi}, {Best}, {B{\^\i}rzan}, {Bonafede},
  {Boonstra}, {Braun}, {Bregman}, {Breitling}, {van de Brink}, {Broderick},
  {Broekema}, {Brouw}, {Br{\"u}ggen}, {Butcher}, {van Cappellen}, {Ciardi},
  {Coenen}, {Conway}, {Coolen}, {Corstanje}, {Damstra}, {Davies}, {Deller},
  {Dettmar}, {van Diepen}, {Dijkstra}, {Donker}, {Doorduin}, {Dromer}, {Drost},
  {van Duin}, {Eisl{\"o}ffel}, {van Enst}, {Ferrari}, {Frieswijk}, {Gankema},
  {Garrett}, {de Gasperin}, {Gerbers}, {de Geus}, {Grie{\ss}meier}, {Grit},
  {Gruppen}, {Hamaker}, {Hassall}, {Hoeft}, {Holties}, {Horneffer}, {van der
  Horst}, {van Houwelingen}, {Huijgen}, {Iacobelli}, {Intema}, {Jackson},
  {Jelic}, {de Jong}, {Juette}, {Kant}, {Karastergiou}, {Koers}, {Kollen},
  {Kondratiev}, {Kooistra}, {Koopman}, {Koster}, {Kuniyoshi}, {Kramer},
  {Kuper}, {Lambropoulos}, {Law}, {van Leeuwen}, {Lemaitre}, {Loose}, {Maat},
  {Macario}, {Markoff}, {Masters}, {McFadden}, {McKay-Bukowski}, {Meijering},
  {Meulman}, {Mevius}, {Middelberg}, {Millenaar}, {Miller-Jones}, {Mohan},
  {Mol}, {Morawietz}, {Morganti}, {Mulcahy}, {Mulder}, {Munk}, {Nieuwenhuis},
  {van Nieuwpoort}, {Noordam}, {Norden}, {Noutsos}, {Offringa}, {Olofsson},
  {Omar}, {Orr{\'u}}, {Overeem}, {Paas}, {Pandey-Pommier}, {Pandey}, {Pizzo},
  {Polatidis}, {Rafferty}, {Rawlings}, {Reich}, {de Reijer}, {Reitsma},
  {Renting}, {Riemers}, {Rol}, {Romein}, {Roosjen}, {Ruiter}, {Scaife}, {van
  der Schaaf}, {Scheers}, {Schellart}, {Schoenmakers}, {Schoonderbeek},
  {Serylak}, {Shulevski}, {Sluman}, {Smirnov}, {Sobey}, {Spreeuw}, {Steinmetz},
  {Sterks}, {Stiepel}, {Stuurwold}, {Tagger}, {Tang}, {Tasse}, {Thomas},
  {Thoudam}, {Toribio}, {van der Tol}, {Usov}, {van Veelen}, {van der Veen},
  {ter Veen}, {Verbiest}, {Vermeulen}, {Vermaas}, {Vocks}, {Vogt}, {de Vos},
  {van der Wal}, {van Weeren}, {Weggemans}, {Weltevrede}, {White}, {Wijnholds},
  {Wilhelmsson}, {Wucknitz}, {Yatawatta}, {Zarka}, {Zensus}, \& {van
  Zwieten}}]{vanHaarlem2013}
{van Haarlem}, M.~P., {Wise}, M.~W., {Gunst}, A.~W., {et~al.} 2013, \aap, 556,
  A2

\bibitem[{{van Loon} {et~al.}(2005){van Loon}, {Cioni}, {Zijlstra}, \&
  {Loup}}]{vanloon2005}
{van Loon}, J.~T., {Cioni}, M.-R.~L., {Zijlstra}, A.~A., \& {Loup}, C. 2005,
  \aap, 438, 273

\bibitem[{{Vassiliadis} \& {Wood}(1993)}]{vassiliadis1993}
{Vassiliadis}, E., \& {Wood}, P.~R. 1993, \apj, 413, 641

\bibitem[{{Verner} {et~al.}(1996){Verner}, {Ferland}, {Korista}, \&
  {Yakovlev}}]{verner1996}
{Verner}, D.~A., {Ferland}, G.~J., {Korista}, K.~T., \& {Yakovlev}, D.~G. 1996,
  \apj, 465, 487

\bibitem[{{Wu} \& {Lee}(1979)}]{wu1979}
{Wu}, C.~S., \& {Lee}, L.~C. 1979, \apj, 230, 621

\bibitem[{{Zarka}(1998)}]{zarka1998}
{Zarka}, P. 1998, \jgr, 103, 20159

\bibitem[{{Zarka} {et~al.}(2004){Zarka}, {Cecconi}, \&
  {Kurth}}]{zarka_et_al2004}
{Zarka}, P., {Cecconi}, B., \& {Kurth}, W.~S. 2004, Journal of Geophysical
  Research (Space Physics), 109, 9

\bibitem[{{Zarka} {et~al.}(2001){Zarka}, {Treumann}, {Ryabov}, \&
  {Ryabov}}]{zarka2001}
{Zarka}, P., {Treumann}, R.~A., {Ryabov}, B.~P., \& {Ryabov}, V.~B. 2001,
  \apss, 277, 293

\end{thebibliography}
